Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-09-10 batchdedup/scheduling.tex
updated scheduling with explanatory figures

A0 does provide for shorter rounds (see Table~\ref{tab:schedule-costs}), but
the efficiency of the packing is poor due to several issues
The first issue is that the round with the current lowest runtime
is chosen. Because backup time is dependent on a combination of the highest
machine load and average machine load, if we add a VM to the currently most
loaded machine in a round it will increase runtime much more than if we add the
VM to a different round where that machine is currently empty
\todo{(insert figure to show how this happens)}. Therefore a better scheduling
would be obtained if we pick the round with the lowest runtime after we
simulate adding the new VM to that round. This new round picking heuristic
takes into account that the same VM might have different affects on different
rounds. This aspect of round picking must be considered because we assume a VM
must be backed
up by the machine that hosts it. If the VMs are located on a DFS such that they
can be
backed up by any machine in the cluster then the problem of load balancing
becomes a simpler but much different problem, and isn't considered here. We
also pick the most heavily loaded (i.e. most data remaing) machine in case of
ties so we can make the most backup progress in a round.

Another improvement we can make to A0 is to the VM picking heuristic. For the
same reason as given above, the largest VM may not always have the greatest
impact on time (e.g. picking a slightly smaller VM on the most heavily loaded
machine has a greater impact than selecting the largest VM on a lightly loaded
machine). A better way to pick VMs than just by size is to simulate removing
VM's, then model the new single round time, and pick the VM whose removal most
decreases the single round time (i.e. the VM that has the greatest impact on
overall backup time). By picking VMs this way we take into account
the machine load in picking which VM to schedule next, and minimize the time
the remaining VMs will take to backup

@@

A1 significantly improves our simulated results, bringing our CoW costs much
closer to the best case than the worst case, as can be seen in
Figure~\ref{tab:schedule-costs}.  Our current implementation of the algorithm
focuses on the deduplication and so doesn't make use of CoW, but we can see
that our simulated times closely match measured runtimes (hopefully). \todo{I
haven't actually implemented the schedulers into the dedup yet to test this}

>>>>

\begin{figure}[thb]
\centering
\includegraphics[width=0.5\textwidth]{images/VMRound.pdf}
\caption{Choosing a round to schedule a VM to. Though the rounds look
identical in terms of total/average load, Round 1 is a much better choice.}
\label{fig:VMRound}
\end{figure}

A0 does provide for shorter rounds (see Table~\ref{tab:schedule-costs}), but
the efficiency of the packing is poor due to several issues
The first issue is that the round with the current lowest runtime
is chosen. Because backup time is dependent on a combination of the highest
machine load and average machine load, if we add a VM to the currently most
loaded machine in a round it will increase runtime much more than if we add the
VM to a different round where that machine is currently empty. You can see this
in Figure~\ref{fig:VMRound}, where VM1D must be scheduled to one of two rounds
which currently have the same average/total load. The effect of VM1D on round 1
would be much less than the effect on round 2 because we wouldn't be increasing
the maximum machine load of the round, so we should schedule to round 1.
Therefore a better
scheduling heuristic is one based on predicted runtime after adding the VM, and
picking the round with the lowest runtime after adding the VM to that round.
This new round picking heuristic
takes into account that the same VM might have different affects on different
rounds. This aspect of round picking must be considered because we assume a VM
must be backed
up by the machine that hosts it. If the VMs are located on a DFS such that they
can be
backed up by any machine in the cluster then the problem of load balancing
becomes a simpler but much different problem, but isn't considered here. We
also pick the most heavily loaded (i.e. most data remaing) machine in case of
ties so we can make the most backup progress in a round, given equivalent
equivalent options.

Another improvement we can make to A0 is to the VM picking heuristic. For the
same reason as given above, the largest VM may not always have the greatest
impact on time (e.g. picking a slightly smaller VM on the most heavily loaded
machine has a greater impact than selecting the largest VM on a lightly loaded
machine). Our improved hueristic to pick VMs is to predict the one-round
runtime after removing that VM, and pick the VM whose removal most
decreases the single round time (i.e. the VM that has the greatest impact on
overall backup time). By picking VMs this way we take into account
the machine load in picking which VM to schedule next, and minimize the time
the remaining VMs will take to backup

@@

A1 significantly improves our simulated results, also bringing our CoW costs
much closer to the best case than the worst case, as can be seen in
Figure~\ref{tab:schedule-costs}.  Our current implementation of the algorithm
focuses on the deduplication and so doesn't make use of CoW, but we can see
that our simulated times closely match measured runtimes (hopefully). \todo{I
haven't actually implemented the schedulers into the dedup yet to test this}
